Lattice Boltzmann simulations of magnetically responsive\\ ellipsoidal particle stabilized emulsions

### 2025-03-11 chapters/paper1.tex

>>>>

This section is based on work published in the Royal Society of Chemistry's Soft Matter journal and
work submited to the American Institude of Physics, Physics of Fluids journal. \cite{karthikeyan_formation_2024} 
It is reproduced from Ref \cite{karthikeyan_formation_2024} with permission from the Royal Society of Chemistry and 
reproduced from submission number \#POF25-AR-DSFD2024-03180, with the permission of AIP Publishing.

### 2025-03-11 chapters/paper2.tex

Sections of this chapter appear in a manuscript submitted to Springer link.
[author and/or editor(s) of contribution], [volume and/or contribution title], [year of publication], [publisher (as it appears on our copyright page)] \
reproduced with permission of Palgrave Springer Nature.

>>>>

Sections of this chapter appear in a manuscript submitted to Springer link as part of the International Conference on Computational 
Science (ICCS) 2025 in the Computing and Data Science for Materials Discovery and Design track, submission number 259 and is
% [author and/or editor(s) of contribution], [volume and/or contribution title], [year of publication], [publisher (as it appears on our copyright page)] \
reproduced with permission of Palgrave Springer Nature.
